Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
credit to adding new two syntax to Haddock goes to us.

Haddock version 2.8 or later provides the {\tt >>>} syntax.
We extended Haddock to support the {\tt prop>} syntax by ourselves
for proof of concept.
The maintainers of Haddock agreed to introduce
the {\tt prop>} syntax and is now supporting it by their own.

@@

We are grateful to David Waern and Simon Marlow
for introducing two new syntax to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that no-parameter properties are tested just once.

>>>>

We implemented the {\tt >>>} syntax and it
is available in Haddock version 2.8 or later.
We also extended Haddock to support the {\tt prop>} syntax
which will be available in the future release.

@@

We are grateful to David Waern, 
one of the Haddock maintainers, 
for reviewing two new syntax to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that no-parameter properties are tested just once.
